Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
rewrite requirements section

To facilitate the adoption and the distribution of the library, we also try to
limit to a bare minimum the set of external dependencies. As such, NumPy and
SciPy -- the two most common dependencies in the Python scientific ecosystem --
are actually the only two required dependencies for the library to fully work.
Some modules may rely on other external libraries, but in such cases we tend to
prefer to directly ship them within the codebase rather than adding new
dependencies for the user to install. In particular, the codebase includes
modified versions of the \textsf{LIBSVM} and \textsf{LIBLINEAR} libraries
\citep{chang2011libsvm,fan2008}, both written in C{}\verb!++! and wrapped using
Cython modules.

>>>>

To facilitate the adoption and the distribution of \sklearn,
the set of external dependencies is kept to a bare minimum:
only Python, NumPy and SciPy are required for a functioning installation.
Binary distributions of these are available for the major platforms.
Visualisation functionality depends on Matplotlib \citep{hunter2007matplotlib}
and/or Graphviz \citep{gansner2000},
but neither is required to do machine learning.
When feasible, external libraries are integrated into the codebase.
In particular, the codebase includes modified versions
of \textsf{LIBSVM} and \textsf{LIBLINEAR}
\citep{chang2011libsvm,fan2008}, both written in C{}\verb!++! and wrapped using
Cython modules.
